Exercise 1: Use sum() to determine the sum of numbers from 2000 to 20000. Provide your code and the actual sum in your answer.

-   code is sum(c(2000:20000)) and answer is 198011000

```{r}
sum(c(2000:20000))
```

```{r}
a <- 5 #assign integer 5 to variable a
b <- 2:20 #assign list of integers 2 through 20 to variable b
a
b
```

Exercise 2: In one or two sentences, describe what the above code snippet did

-   The above code assigned the integer 5 to variable a, and the range of integers from 2 through 20 to variable b. The code then ran the variables a and b to test that this assignment of variables worked.

```{r}
d <- "I just want to be deleted"
d
ls() #will list all variables active
rm(d) #remove object d
ls() #will list all variables, d now removed
#d will be an error 
```

Exercise 3: Add the contents of a and b together and place the results in a new object. Examine the result. Include your code. Try using both sum() and +; do you get different results? If so, why?

```{r}
ab_sum <- sum(a,b) 
ab_plus <- a+b
ab_sum
ab_plus
```

-   sum(a,b) and a+b return different results because the sum function adds all the values represented by a and b together (5 and all the integers between 2 and 20), producing one number; while the function a+b adds the value represented by a (5) to each integer represented in b (2 through 20) individually, producing a vector of 19 numbers.

Exercise 4: What is the sum of the 5th through 10th element of object b? Provide your code and the sum.

-   code is sum(b[5:10]) and answer is 51

```{r}
b[5:10] #check I did the subset right
sum(b[5:10]) #sum the above
```

Exercise 5: What is the sum of the 3rd, 8th, and 10th element of b?

-   code is sum(b[c(3,8,10)]) and answer is 24

```{r}
b[c(3,8,10)] #check, remember concatonate
sum(b[c(3,8,10)])
```

```{r}
m <- matrix(data=1:25,ncol=5,byrow=T)
m
m[5,5]
```

Exercise 6: When extracting from a 2-dimensional object, which number specifies rows and which specifies columns? What does m[3,] do? How can you extract the 3rd, 4th and 5th columns of m together as one object?

-   The first number in the [,] specifies row and the second number specifies column. So m[3,] would return all the values in row 3. m[,c(3,4,5)] would give the values in columns 3, 4, and 5.

```{r}
cbind(m,101:105)
n <- rbind(51:55, m) #add row to the top of m of values 51-55
n #run the above
m[,c(3,4,5)] #remember to leave blank space before comma when extracting columns
```

Exercise 7: What does the cbind command do? How about rbind? Create a new object “n” where the first row is a new row of numbers (your choice) and the following rows are the rows from matrix m. Optional: do the same but reverse the order of the rows from matrix m.

-   cbind adds a column to the matrix and rbind adds a row. The new column or row will be at the beginning or top if the new values come before the matrix object in the parenthetical, and after or at the bottom when the values come after the matrix object.

Exercise 8:

Copy or move your Swirl Notes into the repo, add and commit them.

-   I did not do the swirl tutorial within this project, and when I went to create the project (in order to push things to github), I lost all my data outside of the project. Since I'm running out of time to complete this waiver, I'm not going to redo the swirl tutorial here, but I understand if that results in any sort of deduction.